Supporting Information

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
rob_records <- rob_records[1:166,]

#added a new column HI
df_rob <- rob_records %>%
  select(record_id,author_1, authoryear,quest___1, q3_sar, setting2, 
         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
         risk_of_bias_update_3_complete)
df_rob['setting'] <- NA

@@

#1. "Contact investigation"
contactinvestigation <- q1_rob %>% 
  filter(setting == "Contact investigation" | setting == "Contact investigation, aggregated") %>%
  select(Study, D1, D2, D3, D4, D5, D6)

@@

png("q1_1_new.png", height = 1500, width = 1100)
p3
dev.set(dev.next())
dev.off()

@@

![ROB Q1_1](q1_1_new.png)

>>>>

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
rob_records <- rob_records[rob_records$record_id < "5566", ]

#prepare a dataset
df_rob <- rob_records %>%
  select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
         risk_of_bias_update_3_complete)
df_rob['setting'] <- NA

@@

#1. "Contact investigation" and "Contact investigation, aggregated"
contactinvestigation <- q1_rob %>% 
  filter(setting == "Contact investigation" | setting == "Contact investigation, aggregated") %>%
  select(Study, D1, D2, D3, D4, D5, D6)

@@

dev.new()
png("q1_1_new.png", width = 1000, height = 1500)
p3
graphics.off()

@@

![ROB Q1_1](q1_1_new.png)
![ROB Q1_1](q1_2_new.png)
![ROB Q1_1](q2_new.png)
